---
title: "introduction to LinearRgression"
author: "Yanjie Lyu, Yi Yang"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{introduction to LinearRgression}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

This vignette provides an overview of how to use the LinearRegression for linear regression analysis. We will walk through key functions such as `linreg()`, `coef()`, `plot()`, `pred()`, `print()`, `resid()`, and `summary()`.

## Loading the Package

```{r setup}
library(LinearRegression)
```

## Fitting a Linear Model

```{r}
data(iris)
model <- linreg(Petal.Length~Species, data = iris)
summary(model)

```

In this example, we fit a linear model to the iris data set, predicting Petal.Length based on Sepal.Length and Species. The summary() function provides a detailed report of the model’s coefficients and other statistics.

## Extracting Coefficients

After fitting a model, you can extract the regression coefficients using the `coef()` function.

```{r}
coefficients <- coef(model)
coefficients

```

## Plotting Diagnostics

The `plot()` function generates diagnostic plots to evaluate the model.

```{r}
plot(model)

```

## Making Predictions

You can use the `pred()` function to generate predictions from the fitted model on new data or the original data set.

```{r}
predicted_values <- pred(model)

```

## Accessing Residuals

The `resid()` function extracts the residuals from the fitted model.

```{r}
residuals <- resid(model)
```

## Printing Model Information

The `print()` function provides a simple overview of the fitted model, showing important coefficients and statistics.

```{r}
print(model)

```

# Conclusion

This vignette demonstrated how to use LinearRgression for basic linear regression analysis, from fitting the model to extracting coefficients and generating diagnostic plots.
